$p$-adic precision

### 2014-02-14 padicprec.tex
Working on Section 2

While we have used $\Qp$ throughout this paper for concreteness, all of our results
and suggestions apply to arbitrary complete discrete valuation rings.

@@

@@

We recall usual definitions and properties related to ultrametric 
analysis. We refer to Schneider \cite{Schneider} for a complete 
exposition.

@@

Lemma \ref{lem:main} and Proposition \ref{prop:locanalytic} have 
important applications to effective computations with $p$-adic numbers 
or power series, that we discuss in this Section. Let us recall first 
that a datum involving elements of a complete ultrametric field $K$ 
(\emph{e.g.} $p$-adic numbers or power series) cannot be stored entirely 
on a computed because they basically convey an infinite amount of 
informations. That is why, instead of this datum itself, we generally 
work with neighborhoods of it.

>>>>

@@

We recall some standard definitions from ultrametric analysis, referring to
Schneider \cite{Schneider} for a complete exposition.

Let $K$ be a non-Archimedean local field with absolute value
$|\cdot| : K \to \R_+$ and value group $p^\Z$.   For example, we may take $K = \Qp$ with the
$p$-adic absolute value or $K = \Fp\lb t \rb$ with the $t$-adic absolute value.
Write $\OK$ for the ring of integers of $K$ and choose a dense subring $R \subset K$
consisting of elements that can be represented exactly.  For $K = \Qp$ we may
choose $R = \Z[\frac1p]$ or $R = \Q$; for $K = \Fp\lb t \rb$ we may choose
$R = \Fp[t, t^{-1}]$ or $R = \Fp(t)$.  Choose a collection of subsets $S_h \subset R$
indexed by positive integers $h$ so that
\begin{enumerate}
\item $S_h \subset S_{h+1}$,
\item $\{B_K(x, p^{-h}) : x \in S_h\}$ disjointly covers $K$.
\end{enumerate}
The choice of the $S_h$ is possible since $K$ is non-Archimedean and locally compact.

Let us recall first 
that a datum involving elements of a complete ultrametric field $K$ 
(\emph{e.g.} $p$-adic numbers or power series) cannot be stored entirely 
on a computed because they basically convey an infinite amount of 
informations. That is why, instead of this datum itself, we generally 
work with neighborhoods of it.

@@

@@

Lemma \ref{lem:main} and Proposition \ref{prop:locanalytic} have 
important applications to effective computations with $p$-adic numbers 
or power series, that we discuss in this Section.
